---
title: "Amazon Descriptive Analysis by Data-Cated"
author: "Eirik, Jillian, Nancy, Yifan, Ziyu "
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: cosmo
    toc: yes
    toc_depth: 3
    toc_float: yes
  # pdf_document: 
  #   latex_engine: xelatex
  
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
	fig.width = 8.5,
	message = FALSE,
	warning = FALSE,
	# include = FALSE,
	echo = FALSE
)

options(tinytex.verbose = TRUE)

# Clear environment of variables and functions
rm(list = ls(all = TRUE)) 

# Clear environment of packages
if(is.null(sessionInfo()$otherPkgs) == FALSE) {
  lapply(paste("package:", names(sessionInfo()$otherPkgs), sep=""), 
         detach, character.only = TRUE, unload = TRUE)
}
```


# Install and load Packages

```{r, warning=FALSE, message=FALSE, echo=TRUE}
library(tidyverse)
library(here)
library(skimr)
library(sqldf)
library(gridExtra)
library(fpp2)
library(olsrr)
library(GGally)
library(lubridate)

```


# Load Data

```{r, warning=FALSE, message=FALSE, echo=TRUE}

adoption <- read.csv(file = "../RawData/adoption_final.csv", header=TRUE, sep=",")
april <- read.csv(file = "../RawData/april_billing_final.csv", header=TRUE, sep=",")
may <- read.csv(file = "../RawData/may_billing_final.csv", header=TRUE, sep=",")
june <- read.csv(file = "../RawData/june_billing_final.csv", header=TRUE, sep=",")

```



```{r}
adoption$Geo_Code <- as.character(adoption$Geo_Code)
adoption$Customer_size <- as.factor(adoption$Customer_size)
adoption$Visualize <- as.factor(adoption$Visualize)
adoption$Alert <- as.factor(adoption$Alert)
adoption$Report <- as.factor(adoption$Report)   
adoption$Month <- as.factor(adoption$Month)
adoption$Customer_ID <- as.factor(adoption$Customer_ID)
summary(adoption)
str(adoption)
```


```{r}
# If Geo_code is NA, set it as Geo_unclaimed
adoption <- adoption %>% mutate(Geo_Code2 = ifelse(is.na(Geo_Code), "GEO-UNCLAIMED", Geo_Code))

adoption$Geo_Code <- as.factor(adoption$Geo_Code)

adoption <- adoption %>% select(-Geo_Code)
adoption$Geo_Code2 <- as.factor(adoption$Geo_Code2)
```


Calculating customer's age in months based on registration date and storing in a new column on each table
(takes a while to load, but it works!)

```{r}

elapsed_months <- function(end_date, start_date) {
    ed <- as.POSIXlt(end_date)
    sd <- as.POSIXlt(start_date)
    12 * (ed$year - sd$year) + (ed$mon - sd$mon)
}

april$customer_age <- elapsed_months( april$Billing_month, april$Registration_date)

may$customer_age <- elapsed_months( may$Billing_month, may$Registration_date)

june$customer_age <- elapsed_months( june$Billing_month,june$Registration_date)

```



```{r}
summary(adoption)
```



```{r}
summary(april)
```

```{r}
summary(may)
```

```{r}
summary(june)
```


IDEALLY - add two new columns - total billed for month & count of products billed per customer

having trouble storing output into a new column because grouping by customer-id reduced the number of rows 

could always join the data back into the main table for the month but it seems like there should be a simpler way


APRIL

```{r}
apr_bill_per_cust <- april %>% 
                        group_by(Customer_ID) %>% 
                        summarise(sum(Billed_amount))
apr_bill_per_cust
                              
unique_customer_apr <- distinct(april, Customer_ID)

unique_customer_apr

cust_product_tally_apr <- april %>% 
                        group_by(Customer_ID) %>% 
                        tally()

cust_product_tally_apr

```


MAY

```{r}
may_bill_per_cust <- may %>% 
                        group_by(Customer_ID) %>% 
                        summarise(sum(Billed_amount))
may_bill_per_cust
                   
           
unique_customer_may <- distinct(may, Customer_ID)
unique_customer_may


cust_product_tally_may <- may %>% 
                        group_by(Customer_ID) %>% 
                        tally()
cust_product_tally_may


```

JUNE

```{r}
jun_bill_per_cust <- june %>% 
                        group_by(Customer_ID) %>% 
                        summarise(sum(Billed_amount))
jun_bill_per_cust
                              
unique_customer_jun <- distinct(june, Customer_ID)

unique_customer_jun

cust_product_tally_jun <- june %>% 
                        group_by(Customer_ID) %>% 
                        tally()

cust_product_tally_jun
```

# join table， customer ID as primary key
```{r}
adoptionApril <- adoption %>%
  filter(grepl("April",Month))

AprilAll <- adoptionApril %>% left_join(april , c("Customer_ID" = "Customer_ID"))

adoptionMay <- adoption %>%
  filter(grepl("May",Month))
MayAll <- adoptionMay %>% left_join(may , c("Customer_ID" = "Customer_ID"))

adoptionJune <- adoption %>%
  filter(grepl("June",Month))
JuneAll <-  adoptionJune %>% left_join(june , c("Customer_ID" = "Customer_ID"))

rbind(AprilAll, MayAll, JuneAll)
```

